---
title: "FARS County Data Process"
author: "Blain Morin"
date: "3/19/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(broom)
library(haven)

```


# Summary

* Here is the code that processes the FARS data for the sobriety checkpoint event study.
  * The code starts with the **FARS19752016_clean.dta** located in the "statadata" folder.

* *Note:* Prior to this, I was creating the event study data by joining the FARS data to the UCR data. Since the UCR data may not cover all counties, event study results may be different than what we looked at previously. 


# County Level Data Make
```{r}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")


### Get state identifiers to attach to FARS
state.id = read_csv("accident.CSV") %>% # Read in csv
  select(STATE, STATENAME) %>% # then select state id and state name columns
  group_by(STATENAME) %>% # then group by state
  slice(1) %>% # then grab one observation
  mutate(STATENAME = tolower(STATENAME)) %>% # then make the state names lowercase
  rename(state = STATE) # then rename the state column to lowercase too


### Create dummy variable for MJ Detected
fars = fars %>%
  mutate(mj = ifelse(drugid1 == 605, 1, 0))


### Drunk, drug, and marijuana drivers calculation
fars2 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race, mj) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, county) %>%
  summarise(drunk.drive = sum(vehdrdrive, na.rm = TRUE),
            drug.drive = sum(drugs, na.rm = TRUE),
            mj.drive = sum(mj, na.rm = TRUE)) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))


### Fatalities and n Accidents Calculation
fars3 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(year, STATENAME, county) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))


### Join together and remove missing county observations
county.fars = fars2 %>%
  left_join(fars3) %>%
  drop_na(fips_county_code)


```

# State Level Data Make

```{r}

### Create state level
state.fars = county.fars %>% # take county FARS data
  group_by(state, year) %>% # then group by state-year
  summarise(drunk_drive = sum(drunk.drive), # then sum up the totals for each state-year
            drug_drive = sum(drug.drive),
            mj_drive = sum(mj.drive),
            n_fatalities = sum(fatals),
            n_crashes = sum(n_crashes))

### Attach date sobriety checkpoints turn off
state.fars = state.fars %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))


### Declare treated states
treated_states = c("washington", "wisconsin",
                   "rhode island", "texas",
                   "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")


state.fars = state.fars %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 

state.fars = state.fars %>%
  mutate(timetotreat = replace_na(timetotreat, 0))

state.fars.trim = state.fars %>%
  filter(year %in% 1980:2000)


crashes.model = feols(n_crashes ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = state.fars.trim)

iplot(crashes.model)
  

```



