---
title: "Commented Code for Event Studies"
author: "Blain Morin"
date: "2/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(haven)
library(kableExtra)
library(readxl)

```

# Summary

* This (somewhat lengthy) document shows the steps from the raw data to the event study. 

## Read in and clean UCR arrest data and attach treatment dates

* The treatment date is when the sobriety checkpoints "turned off" or were ruled unconstitutional 

* Lauren, **we should double check these dates** 

```{r}

### Declare treated states
treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

### Initialize a dataframe
df = data.frame()

### The UCR data is broken into years
### This for loop cycles through the declared years and
### concatenates them (flattens to one dataframe)

### 1980 to 2000 captures 6 years before first treatment
### And 6 years after last treatment
for (i in 1980:2000) {
  
  filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
  
  ### Here the variables from UCR data are selected
  temp = readRDS(filename) %>% 
    select(fips_county_code, state, population, agency_name, year, month, starts_with("dui"))
  
  df = rbind(df, temp)
  
}

### Here I group by year and state and
### calculate the total DUI and percent Black DUI by state-year
df.sum = df %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests)) %>%
  ungroup()


### Here I attach the treatment date to the 
### corresponding state
df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  ### Although the month is declared above, we only use the treatyear
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))


df.sum = df.sum %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 


```

As a check, here is what df.sum looks like for two treated states (Texas and Oregon) and one control state (Alabama):

```{r, echo = FALSE}

df.sum.example = df.sum %>%
  filter(state %in% c("texas", "oregon", "alabama")) %>%
  arrange(state)

df.sum.example %>%
  kbl(format = "html", caption = "Two Treated, One Control") %>%
  kable_styling(full_width = FALSE)

```

## Read in and attach FARS data

```{r}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")

### The FARS data only has a numeric state identifier
### Here I use one of the original sets to attach state names
state.id = read_csv("accident.CSV") %>%
  select(STATE, STATENAME) %>%
  group_by(STATENAME) %>%
  slice(1) %>%
  mutate(STATENAME = tolower(STATENAME)) %>%
  rename(state = STATE)

### Drunk driver calculation and drug detected, by state-year
fars2 = fars %>%
  ### These are the selected variables from FARS
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  ### Here I pull out the year from the crashid
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  ### This join attaches the state names
  left_join(state.id) %>%
  ### Groups by state and year and sum the drunk drivers and
  ### drugs detected 
  ### Missing data is dropped from the summation
  group_by(year, STATENAME) %>%
  summarise(drunk.drivers = sum(vehdrdrive, na.rm = TRUE),
            drug.users = sum(drugs, na.rm = TRUE)) %>%
  rename(state = STATENAME)

### Here I calculate the number of fatal accidents and
### The total number of fatalities
fars3 = fars %>%
  ### Select FARS variables
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  ### Extract year from the crash id
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  ### Attach state names
  left_join(state.id) %>%
  ### Here I restrict the data so that there is only
  ### one row for each crash
  ### This avoids double counting of the accident fatalities
  ### The number of fatal accidents is thus the number of rows in each state-year
  group_by(year, STATENAME, crashid) %>%
  ### Takes one observation for each crash id
  slice(1) %>%
  ungroup() %>%
  ### Regroup by state-year and sum
  group_by(year, STATENAME) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME)


### Attach FARS dataframe to the arrest dataframe
df.sum.fars = df.sum %>%
  left_join(fars2) %>%
  left_join(fars3)

```


## Read in and clean state populations for regression weights

* Using the "laws and population.xlsx" file from the Onedrive folder
  * *Assumed to be accurate, though not sure where they came from*


```{r}

### Read in the file
state_populations = read_excel("laws and population.xlsx")

### Select relevant columns
state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

### Rename and clean some columns so that they will join to 
### our UCR and FARS data
state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))


```


## Original method

In prior analyses, I sort of bound the data to only include observations where a treated state
was in the time to treatment interval of +- 6 years:

```{r}

### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

### Here I grab only years where a treated state
### is within +- 6 years
df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)
### The years are stored in the vector rel.dates
rel.dates = df3$fyear


### If a treated state is present but outside of the +- 6
### interval I change it to zero which essentially puts it back into the control group
df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))


### This joins in the state populations
df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)

### Make control states time to treat = 0
### this does not impact the interaction terms of interest

df4 = df4 %>%
  mutate(timetotreat = replace_na(df4$timetotreat, 0))

```

For example (using the same Texas, Oregon, and Alabama subset as above), here is the original method data frame:

```{r, echo = FALSE}

df4.example = df4 %>%
  filter(state %in% c("texas", "oregon", "alabama")) %>%
  arrange(state)

df4.example %>%
  kbl(format = "html", caption = "Original Method") %>%
  kable_styling(full_width = FALSE)

```

This method results in this event study:

```{r, fig.height=5, fig.width=7, echo = TRUE}

crashes.model = feols(n_crashes ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(crashes.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes, Original Method')

```


## Accumulate into End Points

In this version, the lags and leads greater than 6 are treated as -6 and 6, respectively.

This looks more like the data used in the STATA manual for eventdd.

```{r}

### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

# ### Here I grab only years where a treated state
# ### is within +- 6 years
# df3 = df2 %>%
#   filter(treated == 1) %>%
#   filter(timetotreat >= -6 & timetotreat <= 6)
# ### The years are stored in the vector rel.dates
# rel.dates = df3$fyear


### If a treated state is present but outside of the +- 6
### interval I change it to zero which essentially puts it back into the control group
df4 = df2 %>%
  #filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, -6, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 6, timetotreat))


### This joins in the state populations
df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)

### Make control states time to treat = 0
### this does not impact the interaction terms of interest

df4 = df4 %>%
  mutate(timetotreat = replace_na(df4$timetotreat, 0))

```

Here is the example data frame:

```{r, echo = FALSE}

df4.example = df4 %>%
  filter(state %in% c("texas", "oregon", "alabama")) %>%
  arrange(state)

df4.example %>%
  kbl(format = "html", caption = "Original Method") %>%
  kable_styling(full_width = FALSE)

```

And the resulting event study:

```{r, fig.height=5, fig.width=7, echo = TRUE}

crashes.model = feols(DUI_Total ~ i(timetotreat, treated, ref = -1) + population | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(crashes.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes, Accumulate in Endpoints')

```

## All lags and leads included

This version does no binning or capping of the lags and leads (although it is sort of done by the year selection... not sure if we want to run it all the way back to the start of the arrest / crash data anyway). 

```{r}

### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

# ### Here I grab only years where a treated state
# ### is within +- 6 years
# df3 = df2 %>%
#   filter(treated == 1) %>%
#   filter(timetotreat >= -6 & timetotreat <= 6)
# ### The years are stored in the vector rel.dates
# rel.dates = df3$fyear


### If a treated state is present but outside of the +- 6
### interval I change it to zero which essentially puts it back into the control group
df4 = df2 #%>%
  #filter(fyear %in% rel.dates) %>%
  #mutate(timetotreat = ifelse(timetotreat < -6, -6, timetotreat)) %>%
  #mutate(timetotreat = ifelse(timetotreat > 6, 6, timetotreat))


### This joins in the state populations
df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)

### Make control states time to treat = 0
### this does not impact the interaction terms of interest

df4 = df4 %>%
  mutate(timetotreat = replace_na(df4$timetotreat, 0))

```

Here is the example data frame:

```{r, echo = FALSE}

df4.example = df4 %>%
  filter(state %in% c("texas", "oregon", "alabama")) %>%
  arrange(state)

df4.example %>%
  kbl(format = "html", caption = "Original Method") %>%
  kable_styling(full_width = FALSE)

```

And the resulting event study:

```{r, fig.height=5, fig.width=7, echo = TRUE}

crashes.model = feols(n_crashes ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(crashes.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes, All Lags/Leads')

```


Here I add [Sun and Abraham](https://www.sciencedirect.com/science/article/pii/S030440762030378X) corrections for heterogeneous treatment effects. 

```{r, fig.height=5, fig.width=7, echo = TRUE}

df4 = df4 %>%
  mutate(treatyear = replace_na(treatyear, 1000))



crashes.model.sun = feols(n_crashes ~ sunab(treatyear, year) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(list(crashes.model, crashes.model.sun),
      sep = .5,
      ref.line = -1,
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes, All Lags/Leads')


```







