---
title: "Meeting"
author: "Blain Morin"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(haven)

```

# Remake fatality graphic with year 1 as reference

```{r}

states = c("WA", "WI", "RI", "OH", "TX", "ID", "IA", "MI", "MN", "OR")
treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

df = data.frame()

for (i in 1978:2005) {
  
  filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
  
  temp = readRDS(filename) %>%
    select(fips_county_code, state, population, agency_name, year, month, starts_with("dui"))
  
  df = rbind(df, temp)
  
}


df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(treated = replace_na(treated, 0))


```


```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

```


```{r}

library(readxl)
state_populations = read_excel("laws and population.xlsx")

state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)


```



```{r}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")

fars = fars %>%
  mutate(weed = ifelse(drugid1 == 605, 1, 0))


### Get state identifiers to attach to FARS
state.id = read_csv("accident.CSV") %>%
  select(STATE, STATENAME) %>%
  group_by(STATENAME) %>%
  slice(1) %>%
  mutate(STATENAME = tolower(STATENAME)) %>%
  rename(state = STATE)

### Drunks and druggies calculation
fars2 = fars %>%
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race, weed) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME) %>%
  summarise(drunks = sum(vehdrdrive, na.rm = TRUE),
            druggies = sum(drugs, na.rm = TRUE),
            potheads = sum(weed, na.rm = TRUE)) %>%
  rename(state = STATENAME)

### 
fars3 = fars %>%
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(year, STATENAME) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME)



```


```{r}

df.sum.fars = df.sum %>%
  left_join(fars2) %>%
  left_join(fars3)

```


```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)

```


```{r, fig.height=5, fig.width=7, echo = TRUE}

fatal.model = feols(fatals ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)
check = df4 %>%
  filter(timetotreat == 0)


iplot(fatal.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Driving Fatalaties')

```

```{r, fig.height=5, fig.width=7, echo = TRUE}

crashes.model = feols(n_crashes ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(crashes.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes')

```

```{r, fig.height=5, fig.width=7, echo = TRUE}

drunks.model = feols(drunks ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(drunks.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes, Alchohol Detected')

```


# County Effect Size Versus Prior Fatal Crashes

* The graphs in this section intend to answer the question: Prior to the sobriety checkpoints turning off, were they being conducted in areas with a high propensity to drunk drive?

* Recap: $\Delta$ is the percent change in the outcome before and after the checkpoints turned off (6 year average on either side)

$$\Delta = \frac{\bar{X_{after}} - \bar{X_{before}}}{\bar{X_{before}}}$$

```{r}

df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state, fips_county_code) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) /(sum(dui_tot_arrests)+1)) %>%
  ungroup()

population.appendage = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  filter(population != 0) %>%
  group_by(year, state, fips_county_code, agency_name) %>% 
  slice(1) %>%
  ungroup() %>%
  group_by(year, state, fips_county_code) %>%
  mutate(county_population = sum(population)) %>%
  ungroup() %>%
  group_by(fips_county_code, state) %>%
  select(fips_county_code, state, year, county_population) %>%
  summarise(countypopulation = mean(county_population, na.rm = TRUE))
  
  
  

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))

### Drunks and druggies calculation
fars2 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race, weed) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, county) %>%
  summarise(drunks = sum(vehdrdrive, na.rm = TRUE),
            druggies = sum(drugs, na.rm = TRUE),
            potheads = sum(weed, na.rm = TRUE)) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))

### Fatal and Accidents Calculation
fars3 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(year, STATENAME, county) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))



df.sum.fars = df.sum %>%
  left_join(fars2) %>%
  left_join(fars3)


nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

appendage = df3 %>% 
  filter(timetotreat == -5) %>%
  mutate(fatal_crash_5y_prior = n_crashes) %>%
  select(state, fips_county_code, n_crashes, DUI_Total)
  

df4 = df3 %>%
  mutate(after = ifelse(timetotreat > 0, "after", "before")) %>%
  group_by(state, fips_county_code, after) %>%
  summarise(ave_dui = mean(DUI_Total, na.rm = TRUE)) %>%
  spread(key = after, value = ave_dui) %>%
  mutate(delta = (after - before) / after)


df5 = df4 %>%
  left_join(appendage) %>%
  left_join(population.appendage)

df5 %>%
  ggplot(aes(y = delta, x = log(n_crashes))) +
  geom_point(alpha = .6) + 
  facet_wrap(~state) +
  ylim(-4, 1) +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Fatal Crashes (5 years before) Versus Delta Total DUI")


```

```{r}

df5 %>%
  ggplot(aes(y = delta, x = log(DUI_Total))) +
  geom_point(alpha = .6) + 
  facet_wrap(~state) +
  ylim(-4, 1) +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Total DUIs (Five years prior) Versus Delta Total DUI")


```



```{r}

df5 %>%
  mutate(duipercent = DUI_Total / countypopulation) %>%
  ggplot(aes(y = delta, x = log(duipercent))) +
  geom_point(alpha = .6) + 
  facet_wrap(~state) +
  ylim(-4, 1) +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Total % DUIs (Five years prior) Versus Delta Total DUI")


```


# Redo previous Graphics

* I fixed an error in the county population calculation

```{r}

df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state, fips_county_code) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) /(sum(dui_tot_arrests)+1)) %>%
  ungroup()

population.appendage = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  filter(population != 0) %>%
  group_by(year, state, fips_county_code, agency_name) %>% 
  slice(1) %>%
  ungroup() %>%
  group_by(year, state, fips_county_code) %>%
  mutate(county_population = sum(population)) %>%
  ungroup() %>%
  group_by(fips_county_code, state) %>%
  select(fips_county_code, state, year, county_population) %>%
  summarise(countypopulation = mean(county_population, na.rm = TRUE))

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))

### Drunks and druggies calculation
fars2 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race, weed) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, county) %>%
  summarise(drunks = sum(vehdrdrive, na.rm = TRUE),
            druggies = sum(drugs, na.rm = TRUE),
            potheads = sum(weed, na.rm = TRUE)) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))

### Fatal and Accidents Calculation
fars3 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(year, STATENAME, county) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))



df.sum.fars = df.sum %>%
  left_join(fars2) %>%
  left_join(fars3)


nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

df4 = df3 %>%
  mutate(after = ifelse(timetotreat > 0, "after", "before")) %>%
  group_by(state, fips_county_code, after) %>%
  summarise(ave_dui = mean(DUI_Total, na.rm = TRUE)) %>%
  spread(key = after, value = ave_dui) %>%
  mutate(delta = (after - before) / after)


df5 = df4 %>%
  left_join(population.appendage)

df5 %>%
  filter(countypopulation > 0) %>%
  ggplot(aes(y = delta, x = log(countypopulation))) +
  geom_point(alpha = .6) + 
  facet_wrap(~state) +
  ylim(-4, 1) +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("County Population Versus Delta Total DUI")


```


```{r}

df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

df4 = df3 %>%
  mutate(after = ifelse(timetotreat > 0, "after", "before")) %>%
  group_by(state, fips_county_code, after) %>%
  summarise(ave_p.black = mean(DUI_p.Black, na.rm = TRUE)) %>%
  spread(key = after, value = ave_p.black) %>%
  mutate(delta = (after - before) / after)


df5 = df4 %>%
  left_join(population.appendage)

df5 %>%
  filter(countypopulation > 0) %>%
  ggplot(aes(y = delta, x = log(countypopulation))) +
  geom_point(alpha = .6) + 
  facet_wrap(~state) +
  ylim(-4, 1) +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("County Population Versus Delta p Black DUI")




```



```{r}

df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

df4 = df3 %>%
  mutate(after = ifelse(timetotreat > 0, "after", "before")) %>%
  group_by(state, fips_county_code, after) %>%
  summarise(ave_crash = mean(n_crashes, na.rm = TRUE)) %>%
  spread(key = after, value = ave_crash) %>%
  mutate(delta = (after - before) / after)


df5 = df4 %>%
  left_join(population.appendage)

df5 %>%
  filter(countypopulation > 0) %>%
  ggplot(aes(y = delta, x = log(countypopulation))) +
  geom_point(alpha = .6) + 
  facet_wrap(~state) +
  ylim(-4, 1) +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("County Population Versus Delta Fatal Crashes")


```