---
title: "County Level FARS"
author: "Blain Morin"
date: "4/8/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(broom)
library(haven)
library(readxl)
library(bacondecomp)
library(did)

```

# Notes:

* Here I've repeated the FARS data analysis at the county level
* The graphs look remarkably similar to the state level - I don't think it helped with the standard errors. I think this is because the number of "cohorts", or treatment groups, doesn't change.
* Here, the panel is unbalanced - I believe this is because there may not be a row for counties that did not have a fatal accident. I can rebalance the panel, but it will take some additional time.
* The graphs looked wonky when adding county population as a control, here I am just showing weighted estimates



# Outcome: Number of Fatal Crashes

```{r}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")

### Get state identifiers to attach to FARS
state.id = read_csv("accident.CSV") %>% # Read in csv
  select(STATE, STATENAME) %>% # then select state id and state name columns
  group_by(STATENAME) %>% # then group by state
  slice(1) %>% # then grab one observation
  mutate(STATENAME = tolower(STATENAME)) %>% # then make the state names lowercase
  rename(state = STATE) # then rename the state column to lowercase too

### Create dummy variable for MJ Detected
fars = fars %>%
  mutate(mj = ifelse(drugid1 == 605, 1, 0)) # 605 is MJ


fars2 = fars %>%
  select(state, county, month, crashid,
         numaccfats, vehdrdrive, drugs, race, mj) %>% # select these columns
  mutate(year = substr(crashid, 1, 4)) %>% # then create year from accident identifier
  mutate(year = as.numeric(year)) %>% # then make year numeric
  left_join(state.id) %>% # then attach state names
  group_by(year, STATENAME, county) %>% # then group by year county and state
  summarise(drunk.drive = sum(vehdrdrive, na.rm = TRUE), # calculate sums of these events
            drug.drive = sum(drugs, na.rm = TRUE),
            mj.drive = sum(mj, na.rm = TRUE)) %>%
  rename(state = STATENAME, fips_county_code = county) %>% # clean up column names
  mutate(fips_county_code = str_pad(fips_county_code, 3,
                                    side = "left", pad = "0")) # Add 0 to FIPS codes

fars3 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>% # group by crash id
  slice(1) %>% # and take one observation (avoids double counting)
  ungroup() %>%
  group_by(year, STATENAME, county) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))

county.fars = fars2 %>%
  left_join(fars3) %>%
  drop_na(fips_county_code)

county.fars = county.fars %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

### Declare treated states
treated_states = c("washington", "wisconsin",
                   "rhode island", "texas",
                   "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

county.fars = county.fars %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 

countypop = read_dta("countypopagerace_19692017.dta") %>%
  group_by(year, stfips, cofips) %>%
  summarise(co.population = sum(population, na.rm = TRUE)) %>%
  rename(fips_county_code = cofips) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))

fips.appendage = state.id %>%
  rename(stfips = state) %>%
  rename(state = STATENAME)

county.fars = county.fars %>%
  left_join(fips.appendage) %>%
  left_join(countypop) %>%
  mutate(stfips = str_pad(stfips, 2, side = "left", pad = "0")) %>%
  mutate(fips = paste0(stfips, fips_county_code))

county.fars = county.fars %>%
  filter(year %in% 1980:2000) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(post = ifelse(timetotreat > 0, 1, 0)) %>%
  rename(treated_blain = treated) %>%
  filter(fips_county_code != "000")

county.fars = county.fars %>%
  ungroup() %>%
  mutate(gname = replace_na(as.numeric(county.fars$treatyear), 0)) %>%
  mutate(gname = ifelse(gname == 1976, 0, gname)) %>%
  mutate(id.numeric = as.numeric(as.factor(fips))) %>%
  drop_na(co.population)
  

```

## Calloway Santanna

```{r}

cs.model2 = att_gt(
  yname = "n_crashes",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  weightsname = "co.population",
  data = county.fars
)

dyn.cs.model2 = aggte(cs.model2, type = "dynamic")

ggdid(dyn.cs.model2) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Calloway Sant'Anna Population Weighted Results")


```

* I am having trouble getting the function that calculates the ATT with the Calloway Santana method to work at the moment. Going to drop these for now, I think that the Sun and Abraham is working better since the figure more closely resembles the uncorrected version (we expect it to be similar from the bacon decomp plots we were looking at earlier). 


## Sun and Abraham

* Black is the simple two way fe
* Red is the SA correction

```{r}

sa.county = county.fars %>%
  mutate(gname2 = ifelse(gname == 0, 10000, gname))


sa.weight.cluster = feols(n_crashes ~ sunab(cohort = gname2,
                                      period = year) |
                    fips + year,
                    cluster = ~fips,
                    weights = sa.county$co.population,
                    data = sa.county)

uncorrected = feols(n_crashes ~ i(timetotreat, treated_blain, ref = -1) | ## Model
                    fips + fyear, ## Fixed Effects
                    cluster = ~fips, ## Se Clustering
                    weights = county.fars$co.population,
                    data = county.fars)

iplot(list(uncorrected, sa.weight.cluster))

summary(sa.weight.cluster, agg = "ATT")

```


* Here the ATT is 13.7. On average, counties where checkpoints turned off experience 13.7 additional fatal accidents.

I'm not sure about the proper comparison to put it in percentage terms.

1. If compared to the average number of fatal crashes across all counties:

```{r, echo = TRUE}

mean_allcounties = mean(county.fars$n_crashes)

mean_allcounties

(13.7 + mean_allcounties) / mean_allcounties

```

* The average number of fatal crashes for counties in the panel is 13.2.
* A 13.7 increase in fatal crashes is 204% more than average.

2. If compared to average fatal crashes in just control counties:

```{r, echo = TRUE}

control_counties = county.fars %>%
  filter(treated_blain == 1)

mean_control = mean(control_counties$n_crashes)

mean_control

(13.7 + mean_control) / mean_control

```

* The average number of fatal crashes in control counties is 11.2
* An increase of 13.7 crashes is 222% higher than the control average.


I think both of these are wrong lol. 


# Outcome: Fatalities

```{r}


sa.weight.cluster = feols(fatals ~ sunab(cohort = gname2,
                                      period = year) |
                    fips + year,
                    cluster = ~fips,
                    weights = sa.county$co.population,
                    data = sa.county)

uncorrected = feols(fatals ~ i(timetotreat, treated_blain, ref = -1) | ## Model
                    fips + fyear, ## Fixed Effects
                    cluster = ~fips, ## Se Clustering
                    weights = county.fars$co.population,
                    data = county.fars)

iplot(list(uncorrected, sa.weight.cluster))

summary(sa.weight.cluster, agg = "ATT")


```

# Outcome: Crashes with drunk driver involved

```{r}


sa.weight.cluster = feols(drunk.drive ~ sunab(cohort = gname2,
                                      period = year) |
                    fips + year,
                    cluster = ~fips,
                    weights = sa.county$co.population,
                    data = sa.county)

uncorrected = feols(drunk.drive ~ i(timetotreat, treated_blain, ref = -1) | ## Model
                    fips + fyear, ## Fixed Effects
                    cluster = ~fips, ## Se Clustering
                    weights = county.fars$co.population,
                    data = county.fars)

iplot(list(uncorrected, sa.weight.cluster))

summary(sa.weight.cluster, agg = "ATT")


```

# Outcome: County fatal accident rate

```{r}

county.fars = county.fars %>%
  mutate(ncrashrate = n_crashes / co.population) %>%
  mutate(fatalsrate = fatals / co.population) %>%
  mutate(drunkrate = drunk.drive / co.population)

sa.county = county.fars %>%
  mutate(gname2 = ifelse(gname == 0, 10000, gname))



sa.weight.cluster = feols(ncrashrate ~ sunab(cohort = gname2,
                                      period = year) |
                    fips + year,
                    cluster = ~fips,
                    weights = sa.county$co.population,
                    data = sa.county)

uncorrected = feols(ncrashrate ~ i(timetotreat, treated_blain, ref = -1) | ## Model
                    fips + fyear, ## Fixed Effects
                    cluster = ~fips, ## Se Clustering
                    weights = county.fars$co.population,
                    data = county.fars)

iplot(list(uncorrected, sa.weight.cluster))

summary(sa.weight.cluster, agg = "ATT")

```

# Outcome: County fatality rate

```{r}

sa.weight.cluster = feols(fatalsrate ~ sunab(cohort = gname2,
                                      period = year) |
                    fips + year,
                    cluster = ~fips,
                    weights = sa.county$co.population,
                    data = sa.county)

uncorrected = feols(fatalsrate ~ i(timetotreat, treated_blain, ref = -1) | ## Model
                    fips + fyear, ## Fixed Effects
                    cluster = ~fips, ## Se Clustering
                    weights = county.fars$co.population,
                    data = county.fars)

iplot(list(uncorrected, sa.weight.cluster))

summary(sa.weight.cluster, agg = "ATT")

```

# Outcome: Crashes with drunk driver involved rate

```{r}


sa.weight.cluster = feols(drunkrate ~ sunab(cohort = gname2,
                                      period = year) |
                    fips + year,
                    cluster = ~fips,
                    weights = sa.county$co.population,
                    data = sa.county)

uncorrected = feols(drunkrate ~ i(timetotreat, treated_blain, ref = -1) | ## Model
                    fips + fyear, ## Fixed Effects
                    cluster = ~fips, ## Se Clustering
                    weights = county.fars$co.population,
                    data = county.fars)

iplot(list(uncorrected, sa.weight.cluster))

summary(sa.weight.cluster, agg = "ATT")

```
