---
title: "UCR State Level"
author: "Blain Morin"
date: "5/24/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(did)
library(broom)
library(haven)
library(readxl)
library(data.table)

```

```{r}

### Declare treated states
treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

###################################
### Uniform Crime Reporting (UCR)
###################################

### Initialize a dataframe
# df = data.frame()

### The UCR data is broken into years
### This for loop cycles through the declared years and
### concatenates them (flattens to one dataframe)

### 1980 to 2000 captures 6 years before first treatment
### And 6 years after last treatment
# for (i in 1980:2000) {
#   
#   filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
# 
#   ### Here the variables from UCR data are selected
#   temp = readRDS(filename) %>%
#     select(fips_county_code,
#            state, population,
#            agency_name,
#            fips_place_code,
#            population_group,
#            year,
#            month,
#            starts_with("dui"),
#            number_of_months_reported,
#            starts_with("poss_cannabis"),
#            starts_with("poss_drug_total"),
#            starts_with("drunkenness"),
#            starts_with("total_drug")
#            )
# 
#   df = rbind(df, temp)
# 
# }
# 
# fwrite(df, file = "ucr1980_2000.csv")

df = fread("ucr1980_2000.csv")

```

# State Level

## All agencies

### Outcome: DUI Arrest Count

```{r}

### Here I group by year, state, and agency and
### calculate the total DUI
df.sum = df %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_Total_White = sum(dui_tot_white),
            DUI_Total_Black = sum(dui_tot_black),
            Prop_Arrests_Black_DUI = DUI_Total_Black / DUI_Total,
            Prop_Arrests_White_DUI = DUI_Total_White / DUI_Total,
            Prop_Arrests_Other_DUI = (DUI_Total - DUI_Total_White - DUI_Total_Black) / DUI_Total,

            Poss_Cann_Total = sum(poss_cannabis_tot_arrests),
            Poss_Cann_White = sum(poss_cannabis_tot_white),
            Poss_Cann_Total_Black = sum(poss_cannabis_tot_black),

            Poss_Drug_Total = sum(poss_drug_total_tot_arrests),
            Poss_Drug_Total_Black = sum(poss_drug_total_tot_black),
            
            Total_Drug_Total = sum(total_drug_tot_arrests),
            Total_Drug_White = sum(total_drug_tot_white),
            Total_Drug_Black = sum(total_drug_tot_black),
            
            Drunkenness_Total = sum(drunkenness_tot_arrests),
            Drunkenness_White = sum(drunkenness_tot_white),
            Drunkenness_Black = sum(drunkenness_tot_black)
            
            
            ) %>%
  ungroup()


df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  ### Although the month is declared above, we only use the treatyear
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 


### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum %>%
  filter(!state %in% nonstate)

### Attach state weights
### Read in the file
state_populations = read_excel("laws and population.xlsx")

### Select relevant columns
state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

### Rename and clean some columns so that they will join to 
### our UCR and FARS data
state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df3 = df2 %>%
  left_join(state_populations) %>%
  drop_na(population) 

df3 = df3 %>%
  mutate(timetotreat = replace_na(df3$timetotreat, 0)) %>%
  mutate(post = ifelse(timetotreat > 0, 1, 0)) %>%
  rename(treated_alt = treated)

df3 = df3 %>%
  mutate(gname = replace_na(as.numeric(df3$treatyear), 0)) %>%
  mutate(id.numeric = as.numeric(as.factor(state))) %>%
  filter(DUI_Total > 0)

countypop = read_dta("countypopagerace_19692017.dta")

statepops = countypop %>%
  filter(year %in% 1980:2000) %>%
  group_by(year, stfips, race) %>%
  summarise(population = sum(population))

state.id = read_csv("accident.CSV") %>% # Read in csv
  select(STATE, STATENAME) %>% # then select state id and state name columns
  group_by(STATENAME) %>% # then group by state
  slice(1) %>% # then grab one observation
  mutate(STATENAME = tolower(STATENAME)) %>% # then make the state names lowercase
  rename(state = STATE) 

fips.appendage = state.id %>%
  rename(stfips = state) %>%
  rename(state = STATENAME)

statepops = statepops %>%
  left_join(fips.appendage)

statepops = statepops %>%
  spread(race, population) %>%
  rename(white_pop = "1") %>%
  rename(black_pop = "2") %>%
  rename(other_pop = "3")

df4 = df3 %>%
  left_join(statepops) %>%
  mutate(population_nom = population * 1000) %>%
  mutate(dui_rate = DUI_Total / population_nom) %>%
  mutate(white_dui_rate = DUI_Total_White / white_pop) %>%
  mutate(black_dui_rate = DUI_Total_Black / black_pop) %>%
  mutate(Total_Other_DUI = DUI_Total - DUI_Total_White - DUI_Total_Black) %>%
  mutate(other_dui_rate = Total_Other_DUI / other_pop) %>%
  mutate(total_drug_rate = Total_Drug_Total / population_nom) %>%
  mutate(white_drug_rate = Total_Drug_White / white_pop) %>%
  mutate(black_drug_rate = Total_Drug_Black / black_pop) %>%
  mutate(Total_Other_Drug = Total_Drug_Total - Total_Drug_White - Total_Drug_Black) %>%
  mutate(other_drug_rate = Total_Other_Drug / other_pop) %>%
  mutate(Total_Poss_Cann_Rate = Poss_Cann_Total / population_nom) %>%
  mutate(white_cann_rate = Poss_Cann_White / white_pop) %>%
  mutate(black_cann_rate = Poss_Cann_Total_Black / black_pop) %>%
  mutate(Other_Poss_Cann = Poss_Cann_Total - Poss_Cann_White - Poss_Cann_Total_Black) %>%
  mutate(other_cann_rate = Other_Poss_Cann / other_pop) %>%
  mutate(drunkenness_rate = Drunkenness_Total / population_nom) %>%
  mutate(white_drunkenness_rate = Drunkenness_White / white_pop) %>%
  mutate(black_drunkenness_rate = Drunkenness_Black / black_pop) %>%
  mutate(Other_Drunkenness = Drunkenness_Total - Drunkenness_White - Drunkenness_Black) %>%
  mutate(other_drunkenness_rate = Other_Drunkenness / other_pop)


```

```{r}

cs.model = att_gt(
  yname = "DUI_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: DUI Rate

```{r}

cs.model = att_gt(
  yname = "dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("DUI Arrests (Rate, Weighted by State Population)")


```

### Outcome: White DUI Arrest Count

```{r}

cs.model = att_gt(
  yname = "DUI_Total_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: White DUI Arrest Rate

* $Rate = WhiteDUIs / WhitePopulation$

```{r}

cs.model = att_gt(
  yname = "white_dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White DUI Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black DUI Arrests


```{r}

cs.model = att_gt(
  yname = "DUI_Total_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: Black DUI Arrest Rate

* $Rate = BlackDUIs / BlackPopulation$

```{r}

cs.model = att_gt(
  yname = "black_dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black DUI Arrests (Rate, Weighted by State Population)")


```

* Looks like there's an upward effect

### Outcome: Other Race DUI Arrests

```{r}

cs.model = att_gt(
  yname = "Total_Other_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: Other Race DUI Arrest Rate

```{r}

cs.model = att_gt(
  yname = "other_dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race DUI Arrests (Rate, Weighted by State Population)")


```

### Outcome: Proportion White DUIs

$Prop_{white} = WhiteDUI / Total DUI$

```{r}

cs.model = att_gt(
  yname = "Prop_Arrests_White_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Proportion White DUI Arrests (Weighted by State Population)")


```

### Outcome: Proportion Black DUIs

$Prop_{Black} = BlackDUI / Total DUI$

```{r}

cs.model = att_gt(
  yname = "Prop_Arrests_Black_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Proportion Black DUI Arrests (Weighted by State Population)")


```

### Outcome: Proportion Other Race DUIs

$Prop_{Other} = OtherDUI / Total DUI$

```{r}

cs.model = att_gt(
  yname = "Prop_Arrests_Other_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Proportion Other DUI Arrests (Weighted by State Population)")


```

### Outcome: Total Drug Arrests

```{r}

cs.model = att_gt(
  yname = "Total_Drug_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: Total Drug Arrest Rate

$ArrestRate = TotalDrugArrests/Population$

```{r}

cs.model = att_gt(
  yname = "total_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drug Arrests (Rate, Weighted by State Population)")


```

### Outcome: White Drug Arrests


```{r}

cs.model = att_gt(
  yname = "Total_Drug_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: White Drug Arrest Rate

$ArrestRate = WhiteDrugArrests / WhitePopulation$


```{r}

cs.model = att_gt(
  yname = "white_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Drug Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Drug Arrests


```{r}

cs.model = att_gt(
  yname = "Total_Drug_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Drug Arrest Rate

$ArrestRate = BlackDrugArrests / BlackPopulation$


```{r}

cs.model = att_gt(
  yname = "black_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drug Arrests (Rate, Weighted by State Population)")


```


### Outcome: Other Race Drug Arrests


```{r}

cs.model = att_gt(
  yname = "Total_Other_Drug",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: Other Race Drug Arrest Rate

$ArrestRate = OtherDrugArrests / OtherPopulation$


```{r}

cs.model = att_gt(
  yname = "other_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drug Arrests (Rate, Weighted by State Population)")


```

### Outcome: Total Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Poss_Cann_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: Total Cannabis Possession Arrest Rate

$ArrestRate = TotalCannPosArrests / Population$

```{r}

cs.model = att_gt(
  yname = "Total_Poss_Cann_Rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Poss Cann Arrests (Rate, Weighted by State Population)")


```

### Outcome: White Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Poss_Cann_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total White Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: White Cannabis Possession Arrest Rate

```{r}

cs.model = att_gt(
  yname = "white_cann_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Poss Cannabis Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Poss_Cann_Total_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrest Rate

```{r}

cs.model = att_gt(
  yname = "black_cann_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Poss Cannabis Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Other_Poss_Cann",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrest Rate

```{r}

cs.model = att_gt(
  yname = "other_cann_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Poss Cannabis Arrests (Rate, Weighted by State Population)")


```

### Outcome: Total Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Drunkenness_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: Total Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drunkenness Arrests (Rate, Weighted by State Population)")


```

### Outcome: White Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Drunkenness_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: White Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "white_drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Drunkenness Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Drunkenness_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "black_drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drunkenness Arrests (Rate, Weighted by State Population)")


```

### Outcome: Other Race Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Other_Drunkenness",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: Other Race Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "other_drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drunkenness Arrests (Rate, Weighted by State Population)")


```


## Only Agencies That Report All 12 Months, for Every Year 1980-2000

```{r}

# ### Declare treated states
# treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
#                    "michigan", "minnesota",
#                    "oregon")
# 
# ###################################
# ### Uniform Crime Reporting (UCR)
# ###################################
# 
# ### Initialize a dataframe
# df = data.frame()
# 
# ### The UCR data is broken into years
# ### This for loop cycles through the declared years and
# ### concatenates them (flattens to one dataframe)
# 
# ### 1980 to 2000 captures 6 years before first treatment
# ### And 6 years after last treatment
# for (i in 1980:2000) {
# 
#   filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
# 
#   ### Here the variables from UCR data are selected
#   temp = readRDS(filename) %>%
#     select(fips_county_code,
#            state, population,
#            agency_name,
#            ori9,
#            fips_place_code,
#            population_group,
#            year,
#            month,
#            starts_with("dui"),
#            number_of_months_reported,
#            starts_with("poss_cannabis"),
#            starts_with("poss_drug_total"),
#            starts_with("drunkenness"),
#            starts_with("total_drug")
#            )
# 
#   df = rbind(df, temp)
# 
# }
# 
# fwrite(df, file = "ucr1980_2000.csv")

df = fread("ucr1980_2000.csv")


```


```{r, echo = TRUE}

all.agencies = length(unique(df$ori9))

comp1 = df %>%
  filter(number_of_months_reported == 12) %>%
  group_by(state, ori9) %>%
  summarise(n = n()) %>%
  filter(n == 12*21)

complete.agencies = length(unique(comp1$ori9))

complete.agencies

complete.agencies / all.agencies


```


```{r}

complete.list = unique(comp1$ori9)

```

Only 6.7% of agencies report all months during our time frame. 

```{r}

### Declare treated states
treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

###################################
### Uniform Crime Reporting (UCR)
###################################

### Initialize a dataframe
# df = data.frame()

### The UCR data is broken into years
### This for loop cycles through the declared years and
### concatenates them (flattens to one dataframe)

### 1980 to 2000 captures 6 years before first treatment
### And 6 years after last treatment
# for (i in 1980:2000) {
#   
#   filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
# 
#   ### Here the variables from UCR data are selected
#   temp = readRDS(filename) %>%
#     select(fips_county_code,
#            state, population,
#            agency_name,
#            fips_place_code,
#            population_group,
#            year,
#            month,
#            starts_with("dui"),
#            number_of_months_reported,
#            starts_with("poss_cannabis"),
#            starts_with("poss_drug_total"),
#            starts_with("drunkenness"),
#            starts_with("total_drug")
#            )
# 
#   df = rbind(df, temp)
# 
# }
# 
# fwrite(df, file = "ucr1980_2000.csv")

df = fread("ucr1980_2000.csv")

```


### Outcome: DUI Arrest Count

```{r}

### Here I group by year, state, and agency and
### calculate the total DUI
df.sum = df %>%
  group_by(year, state) %>%
  filter(ori9 %in% complete.list) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_Total_White = sum(dui_tot_white),
            DUI_Total_Black = sum(dui_tot_black),
            Prop_Arrests_Black_DUI = DUI_Total_Black / DUI_Total,
            Prop_Arrests_White_DUI = DUI_Total_White / DUI_Total,
            Prop_Arrests_Other_DUI = (DUI_Total - DUI_Total_White - DUI_Total_Black) / DUI_Total,

            Poss_Cann_Total = sum(poss_cannabis_tot_arrests),
            Poss_Cann_White = sum(poss_cannabis_tot_white),
            Poss_Cann_Total_Black = sum(poss_cannabis_tot_black),

            Poss_Drug_Total = sum(poss_drug_total_tot_arrests),
            Poss_Drug_Total_Black = sum(poss_drug_total_tot_black),
            
            Total_Drug_Total = sum(total_drug_tot_arrests),
            Total_Drug_White = sum(total_drug_tot_white),
            Total_Drug_Black = sum(total_drug_tot_black),
            
            Drunkenness_Total = sum(drunkenness_tot_arrests),
            Drunkenness_White = sum(drunkenness_tot_white),
            Drunkenness_Black = sum(drunkenness_tot_black)
            
            
            ) %>%
  ungroup()


df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  ### Although the month is declared above, we only use the treatyear
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 


### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum %>%
  filter(!state %in% nonstate)

### Attach state weights
### Read in the file
state_populations = read_excel("laws and population.xlsx")

### Select relevant columns
state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

### Rename and clean some columns so that they will join to 
### our UCR and FARS data
state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df3 = df2 %>%
  left_join(state_populations) %>%
  drop_na(population) 

df3 = df3 %>%
  mutate(timetotreat = replace_na(df3$timetotreat, 0)) %>%
  mutate(post = ifelse(timetotreat > 0, 1, 0)) %>%
  rename(treated_alt = treated)

df3 = df3 %>%
  mutate(gname = replace_na(as.numeric(df3$treatyear), 0)) %>%
  mutate(id.numeric = as.numeric(as.factor(state))) %>%
  filter(DUI_Total > 0)

countypop = read_dta("countypopagerace_19692017.dta")

statepops = countypop %>%
  filter(year %in% 1980:2000) %>%
  group_by(year, stfips, race) %>%
  summarise(population = sum(population))

state.id = read_csv("accident.CSV") %>% # Read in csv
  select(STATE, STATENAME) %>% # then select state id and state name columns
  group_by(STATENAME) %>% # then group by state
  slice(1) %>% # then grab one observation
  mutate(STATENAME = tolower(STATENAME)) %>% # then make the state names lowercase
  rename(state = STATE) 

fips.appendage = state.id %>%
  rename(stfips = state) %>%
  rename(state = STATENAME)

statepops = statepops %>%
  left_join(fips.appendage)

statepops = statepops %>%
  spread(race, population) %>%
  rename(white_pop = "1") %>%
  rename(black_pop = "2") %>%
  rename(other_pop = "3")

df4 = df3 %>%
  left_join(statepops) %>%
  mutate(population_nom = population * 1000) %>%
  mutate(dui_rate = DUI_Total / population_nom) %>%
  mutate(white_dui_rate = DUI_Total_White / white_pop) %>%
  mutate(black_dui_rate = DUI_Total_Black / black_pop) %>%
  mutate(Total_Other_DUI = DUI_Total - DUI_Total_White - DUI_Total_Black) %>%
  mutate(other_dui_rate = Total_Other_DUI / other_pop) %>%
  mutate(total_drug_rate = Total_Drug_Total / population_nom) %>%
  mutate(white_drug_rate = Total_Drug_White / white_pop) %>%
  mutate(black_drug_rate = Total_Drug_Black / black_pop) %>%
  mutate(Total_Other_Drug = Total_Drug_Total - Total_Drug_White - Total_Drug_Black) %>%
  mutate(other_drug_rate = Total_Other_Drug / other_pop) %>%
  mutate(Total_Poss_Cann_Rate = Poss_Cann_Total / population_nom) %>%
  mutate(white_cann_rate = Poss_Cann_White / white_pop) %>%
  mutate(black_cann_rate = Poss_Cann_Total_Black / black_pop) %>%
  mutate(Other_Poss_Cann = Poss_Cann_Total - Poss_Cann_White - Poss_Cann_Total_Black) %>%
  mutate(other_cann_rate = Other_Poss_Cann / other_pop) %>%
  mutate(drunkenness_rate = Drunkenness_Total / population_nom) %>%
  mutate(white_drunkenness_rate = Drunkenness_White / white_pop) %>%
  mutate(black_drunkenness_rate = Drunkenness_Black / black_pop) %>%
  mutate(Other_Drunkenness = Drunkenness_Total - Drunkenness_White - Drunkenness_Black) %>%
  mutate(other_drunkenness_rate = Other_Drunkenness / other_pop)


```

```{r}

cs.model = att_gt(
  yname = "DUI_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: DUI Rate

```{r}

cs.model = att_gt(
  yname = "dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("DUI Arrests (Rate, Weighted by State Population)")


```

### Outcome: White DUI Arrest Count

```{r}

cs.model = att_gt(
  yname = "DUI_Total_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: White DUI Arrest Rate

* $Rate = WhiteDUIs / WhitePopulation$

```{r}

cs.model = att_gt(
  yname = "white_dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White DUI Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black DUI Arrests


```{r}

cs.model = att_gt(
  yname = "DUI_Total_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: Black DUI Arrest Rate

* $Rate = BlackDUIs / BlackPopulation$

```{r}

cs.model = att_gt(
  yname = "black_dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black DUI Arrests (Rate, Weighted by State Population)")


```

* Looks like there's an upward effect

### Outcome: Other Race DUI Arrests

```{r}

cs.model = att_gt(
  yname = "Total_Other_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race DUI Arrests (Count, Weighted by State Population)")


```

### Outcome: Other Race DUI Arrest Rate

```{r}

cs.model = att_gt(
  yname = "other_dui_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race DUI Arrests (Rate, Weighted by State Population)")


```

### Outcome: Proportion White DUIs

$Prop_{white} = WhiteDUI / Total DUI$

```{r}

cs.model = att_gt(
  yname = "Prop_Arrests_White_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Proportion White DUI Arrests (Weighted by State Population)")


```

### Outcome: Proportion Black DUIs

$Prop_{Black} = BlackDUI / Total DUI$

```{r}

cs.model = att_gt(
  yname = "Prop_Arrests_Black_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Proportion Black DUI Arrests (Weighted by State Population)")


```

### Outcome: Proportion Other Race DUIs

$Prop_{Other} = OtherDUI / Total DUI$

```{r}

cs.model = att_gt(
  yname = "Prop_Arrests_Other_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Proportion Other DUI Arrests (Weighted by State Population)")


```

### Outcome: Total Drug Arrests

```{r}

cs.model = att_gt(
  yname = "Total_Drug_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: Total Drug Arrest Rate

$ArrestRate = TotalDrugArrests/Population$

```{r}

cs.model = att_gt(
  yname = "total_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drug Arrests (Rate, Weighted by State Population)")


```

### Outcome: White Drug Arrests


```{r}

cs.model = att_gt(
  yname = "Total_Drug_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: White Drug Arrest Rate

$ArrestRate = WhiteDrugArrests / WhitePopulation$


```{r}

cs.model = att_gt(
  yname = "white_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Drug Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Drug Arrests


```{r}

cs.model = att_gt(
  yname = "Total_Drug_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Drug Arrest Rate

$ArrestRate = BlackDrugArrests / BlackPopulation$


```{r}

cs.model = att_gt(
  yname = "black_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drug Arrests (Rate, Weighted by State Population)")


```


### Outcome: Other Race Drug Arrests


```{r}

cs.model = att_gt(
  yname = "Total_Other_Drug",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drug Arrests (Count, Weighted by State Population)")


```

### Outcome: Other Race Drug Arrest Rate

$ArrestRate = OtherDrugArrests / OtherPopulation$


```{r}

cs.model = att_gt(
  yname = "other_drug_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drug Arrests (Rate, Weighted by State Population)")


```

### Outcome: Total Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Poss_Cann_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: Total Cannabis Possession Arrest Rate

$ArrestRate = TotalCannPosArrests / Population$

```{r}

cs.model = att_gt(
  yname = "Total_Poss_Cann_Rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Poss Cann Arrests (Rate, Weighted by State Population)")


```

### Outcome: White Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Poss_Cann_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total White Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: White Cannabis Possession Arrest Rate

```{r}

cs.model = att_gt(
  yname = "white_cann_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Poss Cannabis Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Poss_Cann_Total_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrest Rate

```{r}

cs.model = att_gt(
  yname = "black_cann_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Poss Cannabis Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrests

```{r}

cs.model = att_gt(
  yname = "Other_Poss_Cann",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Poss Cannabis Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Cannabis Possession Arrest Rate

```{r}

cs.model = att_gt(
  yname = "other_cann_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Poss Cannabis Arrests (Rate, Weighted by State Population)")


```

### Outcome: Total Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Drunkenness_Total",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: Total Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drunkenness Arrests (Rate, Weighted by State Population)")


```

### Outcome: White Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Drunkenness_White",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Total Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: White Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "white_drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("White Drunkenness Arrests (Rate, Weighted by State Population)")


```

### Outcome: Black Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Drunkenness_Black",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: Black Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "black_drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Black Drunkenness Arrests (Rate, Weighted by State Population)")


```

### Outcome: Other Race Drunkenness Arrests

```{r}

cs.model = att_gt(
  yname = "Other_Drunkenness",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drunkenness Arrests (Count, Weighted by State Population)")


```

### Outcome: Other Race Drunkenness Arrest Rate

```{r}

cs.model = att_gt(
  yname = "other_drunkenness_rate",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df4
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Other Race Drunkenness Arrests (Rate, Weighted by State Population)")


```






