---
title: "FARS County Data Process"
author: "Blain Morin"
date: "3/23/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(broom)
library(haven)
library(readxl)

```


# Summary

* Here is the code that processes the FARS data for the sobriety checkpoint event study.
  * The code starts with the **FARS19752016_clean.dta** located in the "statadata" folder.

* *Note:* Prior to this, I was creating the event study data by joining the FARS data to the UCR data. Since the UCR data may not cover all counties, event study results may be different than what we looked at previously. 


# County Level Data Make

```{r}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")


### Get state identifiers to attach to FARS
state.id = read_csv("accident.CSV") %>% # Read in csv
  select(STATE, STATENAME) %>% # then select state id and state name columns
  group_by(STATENAME) %>% # then group by state
  slice(1) %>% # then grab one observation
  mutate(STATENAME = tolower(STATENAME)) %>% # then make the state names lowercase
  rename(state = STATE) # then rename the state column to lowercase too


### Create dummy variable for MJ Detected
fars = fars %>%
  mutate(mj = ifelse(drugid1 == 605, 1, 0)) # 605 is MJ


### Drunk, drug, and marijuana drivers calculation
fars2 = fars %>%
  select(state, county, month, crashid,
         numaccfats, vehdrdrive, drugs, race, mj) %>% # select these columns
  mutate(year = substr(crashid, 1, 4)) %>% # then create year from accident identifier
  mutate(year = as.numeric(year)) %>% # then make year numeric
  left_join(state.id) %>% # then attach state names
  group_by(year, STATENAME, county) %>% # then group by year county and state
  summarise(drunk.drive = sum(vehdrdrive, na.rm = TRUE), # calculate sums of these events
            drug.drive = sum(drugs, na.rm = TRUE),
            mj.drive = sum(mj, na.rm = TRUE)) %>%
  rename(state = STATENAME, fips_county_code = county) %>% # clean up column names
  mutate(fips_county_code = str_pad(fips_county_code, 3,
                                    side = "left", pad = "0")) # Add 0 to FIPS codes


### Fatalities and n Accidents Calculation
fars3 = fars %>%
  select(state, county, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>% # group by crash id
  slice(1) %>% # and take one observation (avoids double counting)
  ungroup() %>%
  group_by(year, STATENAME, county) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME, fips_county_code = county) %>%
  mutate(fips_county_code = str_pad(fips_county_code, 3, side = "left", pad = "0"))


### Join together and remove missing county observations
### I am removing the missing county observations, but maybe we 
### Should add them to the state level
county.fars = fars2 %>%
  left_join(fars3) %>%
  drop_na(fips_county_code)


```

# State Level Data Make

```{r}

### Create state level
state.fars = county.fars %>% # take county FARS data
  group_by(state, year) %>% # then group by state-year
  summarise(drunk_drive = sum(drunk.drive), # then sum up the totals for each state-year
            drug_drive = sum(drug.drive),
            mj_drive = sum(mj.drive),
            n_fatalities = sum(fatals),
            n_crashes = sum(n_crashes))

### Attach date sobriety checkpoints turn off
state.fars = state.fars %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))


### Declare treated states
treated_states = c("washington", "wisconsin",
                   "rhode island", "texas",
                   "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")


state.fars = state.fars %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 

write.csv(state.fars, file = "state.fars.NAs.csv") # CSV with missing for time to treat for controls

state.fars = state.fars %>%
  mutate(timetotreat = replace_na(timetotreat, 0))

write.csv(state.fars, file = "state.fars.0s.csv") # CSV with 0 for time to treat for controls

state.fars.trim = state.fars %>%
  filter(year %in% 1980:2000)

write.csv(state.fars, file = "state.fars.1980.2000.csv") # CSV trimmed to only 1980 - 2000
  

```

# Attach State Populations 

```{r}

### Read in the file
state_populations = read_excel("laws and population.xlsx")

### Select relevant columns
state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

### Rename and clean some columns so that they will join to 
### our UCR and FARS data
state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))


state.fars.trim = state.fars.trim %>%
  left_join(state_populations)

```

# Simple non-corrected event study

```{r, fig.height=5, fig.width=7, echo = TRUE}

crashes.model = feols(n_crashes ~ i(timetotreat, treated, ref = -1) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = state.fars.trim$population,
                    data = state.fars.trim)

iplot(crashes.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Fatal Crashes, All Lags/Leads')

```



