---
title: "Meeting, doc 2"
author: "Blain Morin"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(kableExtra)
library(haven)

```

# Medical Marijuana, facet by checkpoint state

```{r}

treated_states = c("alaska", "arizona", "arkansas",
                   "california", "colorado", "connecticut",
                   "delaware", "florida", "hawaii",
                   "illinois", "louisiana", "maine",
                   "maryland", "massachusetts", "michigan",
                   "minnesota", "mississippi", "missouri",
                   "montana", "nevada", "new hampshire",
                   "new jersey", "new mexico", "new york",
                   "north dakota", "ohio", "oklahoma", 
                   "oregon", "pennsylvania", "rhode island",
                   "south dakota", "utah", "vermont",
                   "virginia", "washington", "west virginia")
df = data.frame()

for (i in 1990:2020) {
  
  filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
  
  temp = readRDS(filename) %>%
    select(fips_county_code, state, population, agency_name, year, month, starts_with("dui"))
  
  df = rbind(df, temp)
  
}


df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests + 1)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "alaska", "Mar 1999", NA)) %>%
  mutate(treatdate = ifelse(state == "arizona", "Apr 2011", treatdate)) %>%
  mutate(treatdate = ifelse(state == "arkansas", "Nov 2016", treatdate)) %>%
  mutate(treatdate = ifelse(state == "california", "Nov 1996", treatdate)) %>%
  mutate(treatdate = ifelse(state == "colorado", "June 2001", treatdate)) %>%
  mutate(treatdate = ifelse(state == "connecticut", "June 2012", treatdate)) %>%
  mutate(treatdate = ifelse(state == "delaware", "July 2011", treatdate)) %>%
  mutate(treatdate = ifelse(state == "florida", "Jan 2017", treatdate)) %>%
  mutate(treatdate = ifelse(state == "hawaii", "June 2000", treatdate)) %>%
  mutate(treatdate = ifelse(state == "illinois", "Jan 2014", treatdate)) %>%
  mutate(treatdate = ifelse(state == "louisiana", "Aug 2016", treatdate)) %>%
  mutate(treatdate = ifelse(state == "maine", "Dec 1999", treatdate)) %>%
  mutate(treatdate = ifelse(state == "maryland", "June 2014", treatdate)) %>%
  mutate(treatdate = ifelse(state == "massachusetts", "Jan 2013", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Dec 2008", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "June 2014", treatdate)) %>%
  mutate(treatdate = ifelse(state == "mississippi", "Nov 2020", treatdate)) %>%
  mutate(treatdate = ifelse(state == "missouri", "Dec 2018", treatdate)) %>%
  mutate(treatdate = ifelse(state == "montana", "Nov 2004", treatdate)) %>%
  mutate(treatdate = ifelse(state == "nevada", "Oct 2001", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new hampshire", "July 2013", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new jersey", "Oct 2010", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new mexico", "July 2007", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new york", "July 2014", treatdate)) %>%
  mutate(treatdate = ifelse(state == "north dakota", "Apr 2017", treatdate)) %>%
  mutate(treatdate = ifelse(state == "ohio", "Sep 2016", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oklahoma", "June 2018", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Dec 1998", treatdate)) %>%
  mutate(treatdate = ifelse(state == "pennsylvania", "May 2016", treatdate)) %>%
  mutate(treatdate = ifelse(state == "rhode island", "Jan 2006", treatdate)) %>%
  mutate(treatdate = ifelse(state == "south dakota", "Nov 2020", treatdate)) %>%
  mutate(treatdate = ifelse(state == "utah", "Dec 2018", treatdate)) %>%
  mutate(treatdate = ifelse(state == "vermont", "July 2004", treatdate)) %>%
  mutate(treatdate = ifelse(state == "virginia", "Oct 2020", treatdate)) %>%
  mutate(treatdate = ifelse(state == "washington", "Dec 1998", treatdate)) %>%
  mutate(treatdate = ifelse(state == "west virginia", "Apr 2017", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))


df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))


```


```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))  %>%
  filter(year<2020)

```


```{r}

library(readxl)
state_populations = read_excel("laws and population.xlsx")

state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)


```



```{r}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")

fars = fars %>%
  mutate(weed = ifelse(drugid1 == 605, 1, 0))


### Get state identifiers to attach to FARS
state.id = read_csv("accident.CSV") %>%
  select(STATE, STATENAME) %>%
  group_by(STATENAME) %>%
  slice(1) %>%
  mutate(STATENAME = tolower(STATENAME)) %>%
  rename(state = STATE)

### Drunks and druggies calculation
fars2 = fars %>%
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race, weed) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME) %>%
  summarise(drunks = sum(vehdrdrive, na.rm = TRUE),
            druggies = sum(drugs, na.rm = TRUE),
            potheads = sum(weed, na.rm = TRUE)) %>%
  rename(state = STATENAME)

### 
fars3 = fars %>%
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME, crashid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(year, STATENAME) %>%
  summarise(fatals = sum(numaccfats),
            n_crashes = n()) %>%
  rename(state = STATENAME)



```


```{r}

df.sum.fars = df.sum %>%
  left_join(fars2) %>%
  left_join(fars3)

nocheckpoints = c("alaska",
                  "iowa",
                  "south carolina",
                  "michigan",
                  "minnesota",
                  "oregon",
                  "rhode island",
                  "washington",
                  "idaho",
                  "texas",
                  "wisconsin",
                  "wyoming",
                  "montana")

df.sum.fars = df.sum.fars %>%
  mutate(checkpoint_state = ifelse(state %in% nocheckpoints, 0, 1))

```


```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum.fars %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

df4 = df4 %>%
  left_join(state_populations) %>%
  filter(year < 2020) %>%
  drop_na(population)



```

## Outcome: Total DUI Arrests

### Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -6 & timetotreat <= 6) 

g = df5 %>%
  ggplot(aes(x = timetotreat, y = log(DUI_Total + 1))) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~checkpoint_state) +
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("log Total DUIs") +
  xlab("Time to Treatment (0 = Medical Marijuana Legal)") +
  geom_vline(xintercept = 0, linetype="dashed")

ggplotly(g)

```

## Outcome: Fatal Crashes

### Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -6 & timetotreat <= 6) 

g = df5 %>%
  ggplot(aes(x = timetotreat, y = log(fatals + 1))) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~checkpoint_state) +
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("log Total Fatal Crashes") +
  xlab("Time to Treatment (0 = Medical Marijuana Legal)") +
  geom_vline(xintercept = 0, linetype="dashed")

ggplotly(g)

```

* Some states are cutoff because the current FARS data ends at 2016 (for example, Florida legalizes medical marijuana in 2017)


# Data check tables

* Starting at 1990 here, but can extend back to 1974 if needed

```{r}

table1 = df2 %>%
  left_join(state_populations) %>%
  mutate(DUI_percent = DUI_Total / population) %>%
  mutate(Fatal_percent = fatals / population) %>%
  group_by(state) %>%
  summarise(Average_Year_DUI = mean(DUI_Total, na.rm = TRUE),
            Average_DUI_Percent = mean(DUI_percent, na.rm = TRUE),
            Average_Fatal_Crash = mean(fatals, na.rm = TRUE),
            Average_Fatal_Percent = mean(Fatal_percent, na.rm = TRUE))

table1 %>%
  kable(format = "html", digits = 3) %>%
  kable_styling(full_width = FALSE)
  

```

## Graph DUI percent versus Fatal Crash percent

```{r}

table1 %>%
  ggplot(aes(x = Average_DUI_Percent, y = Average_Fatal_Percent)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  ylab("Average Fatal Crashes as Percent of State Population") +
  xlab("Average DUIs as Percent of State Population")


```

* Seems to be an upward trend, as expected? 