---
title: "Year Arrests, FERC Data"
author: "Blain Morin"
date: "1/26/2022"
output: html_document
---

# Recap

* Redo arrest analysis using +-6 years, instead of using +-12 months

* Run the analysis using FARS crash data

# Arrests

* Drop Wyoming because of the lower bound of arrest data (Wyoming ends in 1975 and arrests data starts at 1974)
  * Maybe model can work with the cutoff, but need to think on it



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

library(tidyverse)
library(lubridate)
library(haven)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 

```


```{r}

states = c("WA", "WI", "RI", "OH", "TX", "ID", "IA", "MI", "MN", "OR")
treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

df = data.frame()

for (i in 1974:2020) {
  
  filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
  
  temp = readRDS(filename) %>%
    select(fips_county_code, state, agency_name, year, month, starts_with("dui"))
  
  df = rbind(df, temp)
  
}


df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))

```

```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

```

## Outcome: Total DUI Arrests

### Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -6 & timetotreat <= 6) %>%
  drop_na()

df5 %>%
  ggplot(aes(x = timetotreat, y = DUI_Total)) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  facet_wrap(~state)+
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("Total DUIs") +
  xlab("Time to Treatment (0 = Checkpoints Ruled Illegal)") +
  geom_vline(xintercept = 0, linetype="dashed")

```


### Event Study

* The control group consists of states that did not ban sobriety checkpoints AND states that did ban them but not within plus or minus 12 months of the law change


```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_Total ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total Dui Arrests')

```

## Outcome: Proportion Black Person DUI arrests 

### Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -6 & timetotreat <= 6) %>%
  drop_na()

df5 %>%
  ggplot(aes(x = timetotreat, y = DUI_p.Black)) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  facet_wrap(~state)+
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("Proportion Black Person DUI") +
  xlab("Time to Treatment (0 = Checkpoints Ruled Illegal)") +
  geom_vline(xintercept = 0, linetype="dashed")

```

### Event Study

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_p.Black ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Proportion Black DUI Arrests')

```

# Crashes

* Using "FARS19752016_clean.dta" from the OneDrive folder

* To get number of drunk drivers, I grouped by state and year, then summed the "vehdrdrive" column
  * Ditto for drugs and the "drugs" column

* For fatalities, I grouped by state, year, and crashid, then sliced 1 observation and summed



```{r, echo = TRUE}

### Read in FARS data
fars = read_dta("FARS19752016_clean.dta")


### Get state identifiers to attach to FARS
state.id = read_csv("accident.CSV") %>%
  select(STATE, STATENAME) %>%
  group_by(STATENAME) %>%
  slice(1) %>%
  mutate(STATENAME = tolower(STATENAME)) %>%
  rename(state = STATE)


fars2 = fars %>%
  select(state, month, crashid, numaccfats, vehdrdrive, drugs, race) %>%
  mutate(year = substr(crashid, 1, 4)) %>%
  mutate(year = as.numeric(year)) %>%
  left_join(state.id) %>%
  group_by(year, STATENAME) %>%
  summarise(drunks = sum(vehdrdrive, na.rm = TRUE),
            druggies = sum(drugs, na.rm = TRUE))



```
