---
title: "Year Arrests, FERC Data"
author: "Blain Morin"
date: "1/25/2022"
output: html_document
---

# Recap

* Redo arrest analysis using +-6 years, instead of using +-12 months

* Run the analysis using FARS crash data

# Arrests

* Drop Wyoming because of the lower bound of arrest data (Wyoming ends in 1975 and arrests data starts at 1974)
  * Maybe model can work with the cutoff, but need to think on it



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 

```


```{r}

states = c("WA", "WI", "RI", "OH", "TX", "ID", "IA", "MI", "MN", "OR")
treated_states = c("washington", "wisconsin", "rhode island", "texas",
                   "wyoming", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

df = data.frame()



df1974 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1974.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1975 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1975.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1976 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1976.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1976 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1976.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1985 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1985.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1986 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1986.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1987 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1987.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1988 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1988.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1989 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1989.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1990 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1990.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1991 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1991.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1992 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1992.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1993 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1993.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1994 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1994.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1995 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1995.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df = rbind(df1974, df1975, df1976,
           df1985, df1986,
       df1987, df1988,
           df1988, df1989, df1990, df1991, df1992,
           df1993, df1994, df1995)

remove(df1974, df1975, df1976,
           df1985, df1986,
       df1987, df1988,
           df1988, df1989, df1990, df1991, df1992,
           df1993, df1994, df1995)
