---
title: "Lauren Meeting"
author: "Blain Morin"
date: "12/21/2021"
output: pdf_document
---

## Notes

* We wanted to find when the "turn off" date for states where sobriety checkpoints are not legal
  * I have filled in the off dates in the spreadsheet
  * Might still need to fill in "turn on" dates
* Ten states explicitly do not permit sobriety checkpoints: Idaho, Iowa, Michigan, Minnesota, Oregon, Rhode Island, Texas, Washington, Wisconsin, and Wyoming


## Events Study: Total DUI Arrests

* As a test, I am using three treated states (treated means they "turned off" checkpoints) and one control state (control means they never turned off checkpoints).

I chose three states were the turn off dates were kind of close to each other: WI, WA, and RI. OH is the control state.

Here is the data structure:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 

```





```{r}

states = c("WA", "WI", "RI", "OH")
treated_states = c("washington", "wisconsin", "rhode island")


df1988 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1988.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1989 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1989.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1990 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1990.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1991 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1991.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1992 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1992.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df = rbind(df1988, df1989, df1990, df1991, df1992)

remove(df1988, df1989, df1990, df1991, df1992)

df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(d, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = my(treatdate))

df.sum = df.sum %>%
  mutate(timetotreat = interval(treatdate, d) %/% months(1)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fd = as.factor(d)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))

```

```{r}

check = head(df.sum, n = 10)
check

```

The main interaction of interest is between the timetotreat and treated variables. 

\newpage

## Outcome: DUI Total Arrests

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_Total ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fd, ## Fixed Effects
                    cluster = ~state + fd, ## Se Clustering
                    data = df.sum)

iplot(dui.model, 
      xlab = 'Time to treatment (Months)',
      main = 'Event study: Total Dui Arrests')

```

\newpage

## Outcome = Proportion DUI arrests that were Black

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_p.Black ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fd, ## Fixed Effects
                    cluster = ~state + fd, ## Se Clustering
                    data = df.sum)

iplot(dui.model, 
      xlab = 'Time to treatment (Months)',
      main = 'Event study: Proportion Black DUI Arrests')

```
