---
title: "Agency Level, Proportion Black DUI Arrests"
author: "Blain Morin"
date: "4/17/2022"
output: html_document
---

* Using UCR data, proportion black DUI arrests = Black DUI Arrests / Total DUI arrests for either the state or the agency

* State level seems like it's working better

* Don't see a significant trend

* Here, the weights are by state (agency level populations are not reliable IMO)

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 
library(did)
library(broom)
library(haven)
library(readxl)

```

# Agency Level

```{r}
### Declare treated states
treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

###################################
### Uniform Crime Reporting (UCR)
###################################

### Initialize a dataframe
df = data.frame()

### The UCR data is broken into years
### This for loop cycles through the declared years and
### concatenates them (flattens to one dataframe)

### 1980 to 2000 captures 6 years before first treatment
### And 6 years after last treatment
for (i in 1980:2000) {

  filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")

  ### Here the variables from UCR data are selected
  temp = readRDS(filename) %>%
    select(fips_county_code,
           state, population,
           agency_name, year,
           month,
           starts_with("dui"),
           number_of_months_reported,
           starts_with("poss_cannabis"),
           starts_with("poss_drug_total"),
           starts_with("drunkenness"),
           starts_with("total_drug")
           )

  df = rbind(df, temp)

}

```

# State Level

```{r}

### Here I group by year, state, and agency and
### calculate the total DUI
df.sum = df %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_Total_Black = sum(dui_tot_black),
            Prop_Black_DUI = DUI_Total_Black / DUI_Total,

            Poss_Cann_Total = sum(poss_cannabis_tot_arrests),
            Poss_Cann_Total_Black = sum(poss_cannabis_tot_black),

            Poss_Drug_Total = sum(poss_drug_total_tot_arrests),
            Poss_Drug_Total_Black = sum(poss_drug_total_tot_black),
            ) %>%
  ungroup()


df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  ### Although the month is declared above, we only use the treatyear
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 


### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum %>%
  filter(!state %in% nonstate)

### Attach state weights
### Read in the file
state_populations = read_excel("laws and population.xlsx")

### Select relevant columns
state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

### Rename and clean some columns so that they will join to 
### our UCR and FARS data
state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df3 = df2 %>%
  left_join(state_populations) %>%
  drop_na(population) 

df3 = df3 %>%
  mutate(timetotreat = replace_na(df3$timetotreat, 0)) %>%
  mutate(post = ifelse(timetotreat > 0, 1, 0)) %>%
  rename(treated_alt = treated)

df3 = df3 %>%
  mutate(gname = replace_na(as.numeric(df3$treatyear), 0)) %>%
  mutate(id.numeric = as.numeric(as.factor(state))) %>%
  filter(DUI_Total > 0)

```

## Calloway and Santanna

```{r, echo = TRUE}

cs.model = att_gt(
  yname = "Prop_Black_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df3
)

```

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("DUI Arrests")


```




## Sun and Abraham Method

* Black is uncorrected, Red is corrected

```{r}

sa.agency = df3 %>%
  mutate(gname2 = ifelse(gname == 0, 10000, gname)) %>%
  filter(DUI_Total > 0)

```

* Model codes:

```{r}

sa.weight.cluster = feols(Prop_Black_DUI ~ sunab(cohort = gname2,
                                      period = year) |
                    as.factor(id.numeric) + fyear,
                    cluster = ~state,
                    weights = sa.agency$population,
                    data = sa.agency)


uncorrected = feols(Prop_Black_DUI ~ i(timetotreat, treated_alt, ref = -1) | ## Model
                    as.factor(id.numeric) + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = sa.agency$population,
                    data = sa.agency)



```

```{r}


iplot(list(uncorrected, sa.weight.cluster))


```

# Agency Level (little wonky looking)

```{r}

### Here I group by year, state, and agency and
### calculate the total DUI
df.sum = df %>%
  group_by(year, state, agency_name) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_Total_Black = sum(dui_tot_black),
            Prop_Black_DUI = DUI_Total_Black / DUI_Total,

            Poss_Cann_Total = sum(poss_cannabis_tot_arrests),
            Poss_Cann_Total_Black = sum(poss_cannabis_tot_black),

            Poss_Drug_Total = sum(poss_drug_total_tot_arrests),
            Poss_Drug_Total_Black = sum(poss_drug_total_tot_black),
            ) %>%
  ungroup()


df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  ### Although the month is declared above, we only use the treatyear
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  ### Make the time to treat column
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  ### Make indicator for treated state
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  ### Make years discrete
  mutate(fyear = as.factor(year)) 


### These are some non-states that are dropped from the analysis
nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

### This filters out the non-states
df2 = df.sum %>%
  filter(!state %in% nonstate)

### Attach state weights
### Read in the file
state_populations = read_excel("laws and population.xlsx")

### Select relevant columns
state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

### Rename and clean some columns so that they will join to 
### our UCR and FARS data
state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df3 = df2 %>%
  left_join(state_populations) %>%
  drop_na(population) 

df3 = df3 %>%
  mutate(timetotreat = replace_na(df3$timetotreat, 0)) %>%
  mutate(post = ifelse(timetotreat > 0, 1, 0)) %>%
  rename(treated_alt = treated)

df3 = df3 %>%
  mutate(gname = replace_na(as.numeric(df3$treatyear), 0)) %>%
  mutate(id.numeric = as.numeric(as.factor(paste0(state,agency_name)))) %>%
  filter(DUI_Total > 0)

```

```{r, echo = FALSE}

cs.model = att_gt(
  yname = "Prop_Black_DUI",
  tname = "year",
  idname = "id.numeric",
  gname = "gname",
  allow_unbalanced_panel = TRUE,
  weightsname = "population",
  data = df3
)

```

## Calloway and Santanna

```{r}

cs.dui = aggte(cs.model, type = "dynamic", na.rm = TRUE)

ggdid(cs.dui) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("DUI Arrests")


```




## Sun and Abraham Method

* Black is uncorrected, Red is corrected

```{r}

sa.agency = df3 %>%
  mutate(gname2 = ifelse(gname == 0, 10000, gname)) %>%
  filter(DUI_Total > 0)

```

* Model codes:

```{r}

sa.weight.cluster = feols(Prop_Black_DUI ~ sunab(cohort = gname2,
                                      period = year) |
                    as.factor(id.numeric) + fyear,
                    cluster = ~state,
                    weights = sa.agency$population,
                    data = sa.agency)


uncorrected = feols(Prop_Black_DUI ~ i(timetotreat, treated_alt, ref = -1) | ## Model
                    as.factor(id.numeric) + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = sa.agency$population,
                    data = sa.agency)



```

```{r}


iplot(list(uncorrected, sa.weight.cluster))


```

