---
title: "Add States"
author: "Blain Morin"
date: "1/18/2022"
output: html_document
---

# Recap

* I have filled in the off dates in the spreadsheet and added these to the data
* Ten states explicitly do not permit sobriety checkpoints: Idaho, Iowa, Michigan, Minnesota, Oregon, Rhode Island, Texas, Washington, Wisconsin, and Wyoming


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 

```


```{r}

states = c("WA", "WI", "RI", "OH", "TX", "WY", "ID", "IA", "MI", "MN", "OR")
treated_states = c("washington", "wisconsin", "rhode island", "texas",
                   "wyoming", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")


df1974 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1974.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1975 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1975.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1976 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1976.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1976 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1976.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1985 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1985.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1986 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1986.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1987 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1987.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1988 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1988.rds") %>%
  filter(state_abb %in% states) %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1989 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1989.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1990 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1990.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1991 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1991.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1992 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1992.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1993 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1993.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1994 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1994.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df1995 = readRDS("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_1995.rds") %>%
  select(fips_county_code, state, agency_name, year, month, starts_with("dui"))

df = rbind(df1974, df1975, df1976,
           df1985, df1986,
       df1987, df1988,
           df1988, df1989, df1990, df1991, df1992,
           df1993, df1994, df1995)

remove(df1974, df1975, df1976,
           df1985, df1986,
       df1987, df1988,
           df1988, df1989, df1990, df1991, df1992,
           df1993, df1994, df1995)

df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(d, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wyoming", "Mar 1975", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate))

df.sum = df.sum %>%
  mutate(timetotreat = interval(treatdate, d) %/% months(1)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fd = as.factor(d)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))

```

```{r}

nonstate = c("canal zone", "guam")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -12 & timetotreat <= 12)

rel.dates = df3$fd

df4 = df2 %>%
  filter(fd %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -12, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 12, 0, timetotreat))



```


# Outcome: Total DUI Arrests

## Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -12 & timetotreat <= 12) %>%
  drop_na()

df5 %>%
  ggplot(aes(x = timetotreat, y = DUI_Total)) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  facet_wrap(~state)+
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("Total DUIs") +
  xlab("Time to Treatment (0 = Checkpoints Ruled Illegal") +
  geom_vline(xintercept = 0, linetype="dashed")

```


* Should change this to proportion of population (something like: arrests per 100,000 people)

## Event Study

* The control group consists of states that did not ban sobriety checkpoints AND states that did ban them but not within plus or minus 12 months of the law change


```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_Total ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fd, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Months)',
      main = 'Event study: Total Dui Arrests')

```


# Outcome: Proportion Black Person DUI arrests 

## Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -12 & timetotreat <= 12) %>%
  drop_na()

df5 %>%
  ggplot(aes(x = timetotreat, y = DUI_p.Black)) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  facet_wrap(~state)+
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("Proportion Black Person DUI") +
  xlab("Time to Treatment (0 = Checkpoints Ruled Illegal") +
  geom_vline(xintercept = 0, linetype="dashed")

```

## Event Study

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_p.Black ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fd, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Months)',
      main = 'Event study: Proportion Black DUI Arrests')

```