---
title: "Lauren Meeting"
author: "Blain Morin"
date: "2/1/2022"
output: html_document
---

### Random links of possible interest

* [Mothers against drunk driving liquor law rating for each state](https://online.flippingbook.com/view/361187/)
  * Might be a good control

* [Pretty good website for sobriety checkpoint status by state](https://www.responsibility.org/alcohol-statistics/state-map/state/georgia/issue/sobriety-checkpoints/)
  * Checkpoints clearly permitted in 38 states
  * Some interesting nuance. For example, checkpoints are legal under Missouri law, but the state budget prohibits funding their administration. 

* [New Hampshire passes a law in 2018 to ban sobriety checkpoints (might be the only case where it turned on then off)](https://www.concordmonitor.com/New-Hampshire-House-passes-ban-on-police-sobriety-checkpoints-15744144#:~:text=House%20passes%20ban%20on%20police%20sobriety%20checkpoints,-Lt.&text=House%20representatives%20passed%20a%20bill,practice%20is%20unconstitutional%20and%20ineffective.)






  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE)

library(tidyverse)
library(lubridate)
library(haven)
library(readr)
library(plotly)
library(ggridges)
library(stargazer)
library(data.table) 
library(fixest) 

```


```{r}

df = data.frame()

for (i in 1974:2020) {
  
  filename = paste0("~/michigan_arrests/data/ucr_arrests_monthly_all_crimes_race_sex_", i, ".rds")
  
  temp = readRDS(filename) %>%
    select(fips_county_code, state, agency_name, year, month, starts_with("dui"))
  
  df = rbind(df, temp)
  
}


```

# Rerun Prior Analysis Using Proportion Hispanic

```{r}


treated_states = c("washington", "wisconsin", "rhode island", "texas", "idaho", "iowa",
                   "michigan", "minnesota",
                   "oregon")

df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests),
            DUI_p.Hispanic = sum(dui_tot_hispanic) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "rhode island", "July 1989", NA)) %>%
  mutate(treatdate = ifelse(state == "washington", "May 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "wisconsin", "Aug 1991", treatdate)) %>%
  mutate(treatdate = ifelse(state == "texas", "June 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "idaho", "June 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "iowa", "May 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "michigan", "Sep 1993", treatdate)) %>%
  mutate(treatdate = ifelse(state == "minnesota", "Aug 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oregon", "Sep 1987", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))


```

```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

```

## Outcome: Proportion Hispanic Person DUI arrests 

### Exploratory Graphic

```{r, fig.width=12, fig.height=10}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -6 & timetotreat <= 6) %>%
  drop_na()

df5 %>%
  ggplot(aes(x = timetotreat, y = DUI_p.Hispanic)) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  facet_wrap(~state)+
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("Proportion Hispanic Person DUI") +
  xlab("Time to Treatment (0 = Checkpoints Ruled Illegal)") +
  geom_vline(xintercept = 0, linetype="dashed")

```


* It's strange that after the cutoff all states are 0. I spot checked some of these years and found that Hispanic totals are 0 for these years. Think it is missing data. 


### Event Study

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_p.Hispanic ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Proportion Hispanic DUI Arrests')

```




# Using "checkpoints ruled legal" as the treatment

* Using 1998 for Mississippi turn on year because of spreadsheet notes saying that this is the first checkpoint case

* If date not found, using Federal Upholding year (1990)
  * Utah


```{r}

treated_states = tolower(c(state.name[c(1, 3:11,
                                      13:14, 16:21, 
                                      24, 27:36,
                                      38, 41, 42,
                                      44:46, 48)],
                         "district of columbia"))



df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests),
            DUI_p.Hispanic = sum(dui_tot_hispanic) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "alabama", "Jan 1987", NA)) %>%
  mutate(treatdate = ifelse(state == "arizona", "Jan 1984", treatdate)) %>%
  mutate(treatdate = ifelse(state == "arkansas", "Jan 1992", treatdate)) %>%
  mutate(treatdate = ifelse(state == "california", "Jan 1987", treatdate)) %>%
  mutate(treatdate = ifelse(state == "colorado", "Jan 1990", treatdate)) %>%
  mutate(treatdate = ifelse(state == "connecticut", "Jan 1996", treatdate)) %>%
  mutate(treatdate = ifelse(state == "delaware", "Jan 1979", treatdate)) %>%
  mutate(treatdate = ifelse(state == "florida", "Jan 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "georgia", "Jan 1984", treatdate)) %>%
  mutate(treatdate = ifelse(state == "hawaii", "Jan 2000", treatdate)) %>%
  mutate(treatdate = ifelse(state == "illinois", "Jan 1985", treatdate)) %>%
  mutate(treatdate = ifelse(state == "indiana", "Jan 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "kansas", "Jan 1983", treatdate)) %>%
  mutate(treatdate = ifelse(state == "kentucky", "Jan 1984", treatdate)) %>%
  mutate(treatdate = ifelse(state == "louisiana", "Jan 2000", treatdate)) %>%
  mutate(treatdate = ifelse(state == "maine", "Jan 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "maryland", "Jan 1984", treatdate)) %>%
  mutate(treatdate = ifelse(state == "massachusetts", "Jan 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "mississippi", "Jan 1998", treatdate)) %>%
  mutate(treatdate = ifelse(state == "nebraska", "Jan 1986", treatdate)) %>%
  mutate(treatdate = ifelse(state == "nevada", "Jan 1987", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new hampshire", "Jan 2003", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new jersey", "Jan 1989", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new mexico", "Jan 1987", treatdate)) %>%
  mutate(treatdate = ifelse(state == "new york", "Jan 1984", treatdate)) %>%
  mutate(treatdate = ifelse(state == "north carolina", "Jan 1983", treatdate)) %>%
  mutate(treatdate = ifelse(state == "north dakota", "Jan 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "ohio", "Jan 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "oklahoma", "Jan 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "pennsylvania", "Jan 1987", treatdate)) %>%
  mutate(treatdate = ifelse(state == "south dakota", "Jan 1994", treatdate)) %>%
  mutate(treatdate = ifelse(state == "tennessee", "Jan 1988", treatdate)) %>%
  mutate(treatdate = ifelse(state == "utah", "Jan 1990", treatdate)) %>%
  mutate(treatdate = ifelse(state == "vermont", "Jan 1985", treatdate)) %>%
  mutate(treatdate = ifelse(state == "virginia", "Jan 1985", treatdate)) %>%
  mutate(treatdate = ifelse(state == "west virginia", "Jan 1995", treatdate)) %>%
  mutate(treatdate = ifelse(state == "district of columbia", "Jan 1991", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))



```

```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

```


## Outcome: Total DUI Arrests

### Exploratory Graphic

```{r, fig.width=12, fig.height=12}

df5 = df2 %>%
  filter(treated == 1) %>% 
  filter(timetotreat >= -6 & timetotreat <= 6) %>%
  drop_na()

df5 %>%
  ggplot(aes(x = timetotreat, y = DUI_Total)) +
  geom_point(aes(color = state)) +
  geom_line(aes(color = state)) +
  facet_wrap(~state)+
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none") +
  ylab("Total DUIs") +
  xlab("Time to Treatment (0 = Checkpoints Upheld)") +
  geom_vline(xintercept = 0, linetype="dashed")

```

* We would expect no effect or a positive effect

* Looks like a negative effect in:
  * California
  * Georgia
  * Kentucky

* Otherwise pretty flat for most states

### Event Study

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_Total ~ i(timetotreat, treated, ref = 0) | ## Model
                      state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total DUI Arrests')

```


### Weighted Event Study

* Using the population file from OneDrive

```{r}

library(readxl)
state_populations = read_excel("laws and population.xlsx")

state_populations = state_populations %>%
  select(`state name`, year, `population (hundreds of thousands)`)

state_populations = state_populations %>%
  rename(state = `state name`) %>%
  rename(population = `population (hundreds of thousands)`) %>%
  mutate(state = tolower(state))

df4 = df4 %>%
  left_join(state_populations) %>%
  drop_na(population)


```

```{r, fig.height=5, fig.width=7, echo = TRUE}

dui.model = feols(DUI_Total ~ i(timetotreat, treated, ref = 0) | ## Model
                    state + fyear, ## Fixed Effects
                    cluster = ~state, ## Se Clustering
                    weights = df4$population,
                    data = df4)

iplot(dui.model, 
      xlab = 'Time to treatment (Years)',
      main = 'Event study: Total DUI Arrests')

```


# Recreational Marijuana Legalization as Treatment

```{r}

treated_states = c("alaska",
                   "arizona",
                   "california",
                   "colorado",
                   "illinois",
                   "maine",
                   "michigan",
                   "montana",
                   "nevada",
                   "new jersey",
                   "oregon",
                   "south dakota",
                   "vermont",
                   "washington")



df.sum = df %>%
  mutate(monthyear = paste(month, year)) %>%
  mutate(d = my(monthyear)) %>%
  group_by(year, state) %>%
  summarise(DUI_Total = sum(dui_tot_arrests),
            DUI_p.Black = sum(dui_tot_black) / sum(dui_tot_arrests),
            DUI_p.Hispanic = sum(dui_tot_hispanic) / sum(dui_tot_arrests)) %>%
  ungroup()

df.sum = df.sum %>%
  mutate(treatdate = ifelse(state == "alaska", "Feb 2015", NA)) %>%
  mutate(treatdate = ifelse(state == "arizona", "Nov 2020", treatdate)) %>%
  mutate(treatdate = ifelse(state == "california", "Nov 2020", treatdate)) %>%
  mutate(treatdate = my(treatdate)) %>%
  mutate(treatyear = format(treatdate, format = "%Y"))

df.sum = df.sum %>%
  mutate(timetotreat = as.numeric(year) - as.numeric(treatyear)) %>%
  mutate(treated = ifelse(state %in% treated_states, 1, 0)) %>%
  mutate(fyear = as.factor(year)) %>%
  mutate(timetotreat = replace_na(timetotreat, 0)) %>%
  mutate(treated = replace_na(treated, 0))



```

```{r}

nonstate = c("canal zone", "guam", "69", "98", "99", "american samoa", "virgin islands", "puerto rico")

df2 = df.sum %>%
  filter(!state %in% nonstate)

df3 = df2 %>%
  filter(treated == 1) %>%
  filter(timetotreat >= -6 & timetotreat <= 6)

rel.dates = df3$fyear

df4 = df2 %>%
  filter(fyear %in% rel.dates) %>%
  mutate(timetotreat = ifelse(timetotreat < -6, 0, timetotreat)) %>%
  mutate(timetotreat = ifelse(timetotreat > 6, 0, timetotreat))

```

